Improving the Efficiency of Dislocality Constraints for an Automated Software Mapping in Safety-Critical Systems

### 2017-12-20 paper.tex
More additions

\subsection*{Combined Values-Union and Instantiation-Only Approach}

>>>>

\subsection*{Combined Union-Variables and Instantiation-Only Approach}

The third approach tries to build upon the instantiation-only approach and improve the strength of its propagation.
For this purpose, a new integer variable $X^\star$ will be added for each list of variables $X = \{X_1, \dots, X_n\}$ that were provided to the advanced \texttt{allDifferent} constraint.
The new variable $X^\star$ will contain the union of the remaining values of all variables in $X$.
This can be achieved with a custom propagator similar to the already existing \texttt{PropSetIntValuesUnion} propagator in Choco 4.

With these new ``union variables'' being available, adding a simple \texttt{allDifferent} constraint linking all of the union variables, should improve propagation.
Please note, that these ``union variables'' must not be added to the list of variables for branching as part of the search strategy in Choco 4 as they will not always be resolved to only \emph{one} value.

This approach will be combined with the instantiation-only approach from the previous section.
However, in comparison to the instantiation-only approach, the handling of union-variables requires the addition of a new variable and a propagator for each list of variables, so there will be some overhead.

Based on the description of these three approaches to implement the semantics of an advanced \texttt{allDifferent} constraint, the next sections will describe experiments conducted by the authors and preliminary results to assess and compare the performance and efficiency of each approach.
